\begin{prop}
	It's impossible that both $f(X_{i-1} \cup \qty{u_i})-f(X_{i-1}) <0$ and  $f(Y_{i-1} \setminus \qty{u_i}) - f(Y_i)<0$.
	\begin{proof}
		From diminishing returns:
		\begin{align}
		f(X_{i-1} \cup \qty{u_i})-f(X_{i-1}) \geq f(Y_i) - f(Y_{i-1} \setminus \qty{u_i})  \\
		f(X_{i-1} \cup \qty{u_i})-f(X_{i-1}) + f(Y_i) - f(Y_{i-1} \setminus \qty{u_i}) \geq 0
		\end{align}
		Thus at least one of  $f(X_{i-1} \cup \qty{u_i})-f(X_{i-1}) $ and  $f(Y_{i-1} \setminus \qty{u_i}) - f(Y_i)$ is greater than $0$.
	\end{proof}
\end{prop}


\begin{lemma}
	Let $S^*$ be an optimal solution and 
	\begin{align}
	S^*_i = S^* \cup X_i \cap Y_i
	\end{align}
	i.e., optimal solution to which we add everything \cref{alg:opt_double_greedy} added and drop everything it dropped.
	
	For all $i$:
	\begin{align}
	\mathbb{E} \qty\bigg[f(S^*_{i-1}) - f(S^*_i)] \leq \mathbb{E} \qty\bigg[f(X_i) - f(X_{i-1})+f(Y_i) - f(Y_{i-1}) ]
	\end{align}
\end{lemma}

\begin{lemma}
	Let $S^*$ be an optimal solution and 
	\begin{align}
	S^*_i = S^* \cup X_i \cap Y_i
	\end{align}
	i.e., optimal solution to which we add everything \cref{alg:rand_double_greedy} added and drop everything it dropped.
	
	For all $i$:
	\begin{align}
	\mathbb{E} \qty\bigg[f(S^*_{i-1}) - f(S^*_i)] \leq \frac{1}{2} \mathbb{E} \qty\bigg[f(X_i) - f(X_{i-1})+f(Y_i) - f(Y_{i-1}) ]
	\end{align}
	
	\begin{proof}
		Take a look at $i^{th}$ iteration and condition on previous iterations:
		\begin{align}
		\mathbb{E} \qty\bigg[ f(X_i) - f(X_{i-1}) + f(Y_i) - f(Y_{i-1}) \bigg\vert X_{i-1}, Y_{i-1}] =\\= \frac{a_i}{a_i+b_i} \underbrace{\qty(f(X_{i-1} \cup \qty{u_i})-f(X_{i-1}))}_{=a_i  \text{ if } a_i\neq 0} + \frac{b_i}{a_i+b_i} \underbrace{\qty(f(Y_{i-1} \cup \qty{u_i})-f(Y_{i-1}))}_{=b_i  \text{ if } b_i\neq 0} = \frac{a_i^2+b_i^2}{a_i+b_i}
		\end{align}
		
		Now divide into two cases: $u_i \in S^*$ and $u_i \notin S^*$.
		
		\begin{itemize}
			\item If $u_i \notin S^*$, in particular, $u_i \notin S^*_{i-1}$:
			\begin{align}
			\mathbb{E} \qty[f(S^*_{i-1})-f(S^*_{i}) ] &= \frac{a_i}{a_{i} + b_{i}} \qty(f(S^*_{i-1}) -f(S^*_{i-1}\cup \qty{u_i})) \stackrel{S^*_{i-1} \subseteq Y_{i-1}\setminus \qty{u_i}}{\leq }\\&\leq \frac{a_i}{a_{i} + b_{i}} \qty(f(Y^*_{i-1}\setminus \qty{u_i}) -f(Y^*_{i-1})) \leq \frac{a_i b_i}{a_i+b_i}
			\end{align}
			\item If $u_i \in S^*$, in particular, $u_i \in S^*_{i-1}$:
			\begin{align}
			\mathbb{E} \qty[f(S^*_{i-1})-f(S^*_{i}) ] &= \frac{b_i}{a_{i} + b_{i}} \qty(f(S^*_{i-1}) -f(S^*_{i-1}\setminus \qty{u_i})) \stackrel{X_{i-1} \subseteq S^*_{i-1} \setminus \qty{u_i}}{\leq }\\&\leq \frac{b_i}{a_{i} + b_{i}} \qty(f(X^*_{i-1}\cup \qty{u_i}) -f(X^*_{i-1})) \leq \frac{a_i b_i}{a_i+b_i}
			\end{align}
		\end{itemize}
		And since $a_i^2-2a_ib_i+b_i^2 = (a_i-b_i)^2 \geq 0$ (and by tower property), we get the required.
		
	\end{proof}
\end{lemma}


\begin{theorem}[\cite{buchbinder2015tight}]
	\vref{alg:rand_double_greedy} is $\frac{1}{2}$ approximation in expectation.
	\begin{proof}
		Denote 
		\begin{align}
			S_{alg} = S^*_n=X_n=Y_n
		\end{align}
		Then
		\begin{align}
		\mathbb{E} \qty\bigg[f(S^*_{0}) - f(S^*_n)] &\leq \frac{1}{2} \mathbb{E} \qty\bigg[f(X_n) - f(X_{0})+f(Y_n) - f(Y_{0}) ]\\
		\mathbb{E} \qty\bigg[f(S^*) - f(S_{alg})] &\leq \frac{1}{2} \mathbb{E} \qty\bigg[2S_{alg} - f(X_{0}) - f(Y_{0}) ]\stackrel{f(S)\geq 0}{\leq} \mathbb{E} \qty\bigg[S_{alg} ]
		\end{align}
		Thus
		\begin{align}
		\mathbb{E} \qty[S_{alg} ] \geq\frac{1}{2}\mathbb{E} \qty[f(S^*)] 
		\end{align}
		
	\end{proof}

\begin{coll}
	\vref{alg:opt_double_greedy} is $\frac{1}{3}$ approximation in expectation.
\end{coll}
\end{theorem}


\paragraph{Note} \vref{alg:rand_double_greedy} runs in $\order{N}$ time.


\section{Knapsack constraints}
Let each element of set have price $c_i$ and budget $B$, then
\begin{align}
\max \: & f(S)\\
\st & \sum_{i \in S} c_i \leq B
\end{align}


\begin{algorithm}
	\caption{}\label{alg:knapsack_greedy}
	\begin{algorithmic}[1]
		\Procedure{Density Greedy}{$N$}
		\State $S \gets \emptyset$
		\While{$N\neq \emptyset$}
		\State $x^* \gets \arg \max \qty{ \frac{f(S\cup \qty{x})-f(S)}{c_i}}$
		\If{$c(S) + c_{x^*} \leq B$}
		\State $S\to S \cup \qty{x^*}$
		\EndIf
		\State $N \gets N\setminus \qty{x^*}$
		\EndWhile
		\State \textbf{return} $S$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

Note that this is generalization of cardinality constraint.


\begin{algorithm}
	\caption{}\label{alg:optimized_knapsack}
	\begin{algorithmic}[1]
		\Procedure{Optimized Density Greedy}{$N$}
		\State $S_1 \gets$ output of \vref{alg:knapsack_greedy}
		\State $S_2 \gets \qty{\arg\max\limits_{\substack{i\in N\\c_i \leq B}} f(i)}$
		\State \textbf{return} $\arg\max\limits_{S\in \qty{S_1,S_2}} f(S)$
		\EndProcedure
	\end{algorithmic}
\end{algorithm}


\begin{prop}[\cite{khuller1999budgeted}]
	\vref{alg:optimized_knapsack} is $\frac{1}{2}\qty(1-\frac{1}{e})$-optimal.
\end{prop}
\begin{prop}
	\vref{alg:optimized_knapsack} is $\qty(1-\frac{1}{\sqrt{e}})$-optimal.
\end{prop}

\begin{theorem}[\cite{khuller1999budgeted,sviridenko2004note}]
	% https://thibaut.horel.org/submodularity/notes/02-12.pdf
	If a set of $l$ most dense items in optimal solution $S^*$, it is possible to get good approximation to the optimal solution.
	
	Enumerating all sets of up to 3 most dense items in optimal solution $S^*$, we can acquire $1-\frac{1}{e}$-approximation of optimal solution. Since cardinality constraint is a particular case of knapsack constraint, this is best polynomial approximation.
\end{theorem}